Scheduling and Amortization for MPC

### 2021-12-31 paper_SIMD.tex
Fixed some typos in Vectorization seciton.

\STATE \COMMENT {Begin of outer loop $i$.}
\STATE {$\texttt{index}_0 = \phi(\texttt{index}_1, -1)$} 
\STATE {$\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$}

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$}
\STATE {$\texttt{d} = \mathit{SUB}(\texttt{S}[i,j], \texttt{C}[j])$}
\STATE {$\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$}
\STATE {$\texttt{sum}_1 = \texttt{ADD}(\texttt{sum}_0,\texttt{p})$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{c} = \mathit{CMP}(\texttt{sum}_0,\texttt{min}_0)$}
\STATE {$\texttt{index}_1 = \mathit{MUX}(\texttt{c},\texttt{index}_0,i)$}
\STATE {$\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{min}_0,\texttt{sum}_0)$}
\STATE \COMMENT {End of outer loop $i$.}

@@

\STATE \COMMENT {Begin of outer loop $i$.}
\STATE {$\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$} 
\STATE {$\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$}

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j-1], [0,0,...])$}
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUB}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{sum}'_0[i] = \mathit{drop\_dim}(\texttt{sum}_0[i,j],j)$}
\STATE {$\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_0[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}])$}
\STATE {$\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N])$}
\STATE {$\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_0[\stackrel{\rightarrow}{i}])$}
\STATE \COMMENT {End of outer loop $i$.}

@@

Starting at the inner phi-node $\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j], [0,0,...])$, the algorithm first computes its closure. The closure amounts to the phi-node itself and $\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$, accounting for the loop-carried dependency of the computation of \texttt{sum}. The algorithm replaces this closure with a FOR loop on $j$ removing vectoriaztion on $j$. Note that the SUB and MUL computations remain outside of the loop as they do not depend on phi-nodes that are part of cycles. The algorithm adds same-level edges, one from $\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = ...$ to the monolithic FOR-loop node, and one from the FOR-loop node to $\texttt{c}[\stackrel{\rightarrow}{i}] = ...$.

@@

\STATE \COMMENT {Begin of outer loop $i$.}
\STATE {$\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$} 
\STATE {$\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$}

@@

\STATE \COMMENT {Begin of inner loop $j$. Loop is now much "shorter"!}
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j], [0,0,...])$}
\STATE {FOR j=0; j<=D; j++} \COMMENT{ Will turn into a MOTION loop.}
\STATE \hspace{0.25cm}{$\texttt{sum}_1[\stackrel{\rightarrow}{i},{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},{j}],\texttt{p}[\stackrel{\rightarrow}{i},{j}])$}
\STATE \COMMENT {End of inner loop $j$.}

@@

Next, analysis moves to outer dimension $i$. There are two phi-nodes, $\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$ and $\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$.
The closure of the first is 
\[
\begin{array}{l}
\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000) \\
\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_0[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_0[\stackrel{\rightarrow}{i}])
\end{array}
\]
and the closure of the second one is
\[
\begin{array}{l}
\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1), \\ 
%\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N]) 
\end{array}
\]

@@

\STATE 
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUB\_SIMD}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL\_SIMD}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$} \\
\STATE {} 
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j-1], [0,0,...])$}
\STATE {FOR j=0; j<=D; j++} \COMMENT{ Turns into a MOTION loop, was $j$-loop.}
\STATE \hspace{0.25cm}{$\texttt{sum}_1[\stackrel{\rightarrow}{i},{j}] = \mathit{ADD\_SIMD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},{j}],\texttt{p}[\stackrel{\rightarrow}{i},{j}])$}
\STATE {} 
\STATE {$\texttt{sum}'_0[i] = \mathit{drop\_dim}(\texttt{sum}_0[i,j],j)$}
\STATE {} 
\STATE {$\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$}
\STATE {FOR i=0; i<=N; i++} \COMMENT{ Turns into a MOTION loop, was $i$-loop.}
\STATE \hspace{0.25cm}{$\texttt{c}[{i}] = \mathit{CMP}(\texttt{sum}'_0[{i}],\texttt{min}_0[{i}])$}
\STATE \hspace{0.25cm}{$\texttt{min}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{min}_0[{i}],\texttt{sum}'_1[{i}])$}
\STATE {}
\STATE {$\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$} 
\STATE {FOR i=0; i<=N; i++} \COMMENT{ Turns into a MOTION loop, was $i$-loop.}
\STATE \hspace{0.25cm}{$\texttt{index}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{index}_0[{i}],i)$}

>>>>

\STATE \COMMENT {Begin of outer loop $i$.}
\STATE {$\texttt{index}_0 = \phi(-1, \texttt{index}_1)$} 
\STATE {$\texttt{min}_0 = \phi(10000,\texttt{min}_1)$}

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0 = \phi(0, \texttt{sum}_1)$}
\STATE {$\texttt{d} = \mathit{SUB}(\texttt{S}[i,j], \texttt{C}[j])$}
\STATE {$\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$}
\STATE {$\texttt{sum}_1 = \texttt{ADD}(\texttt{sum}_0,\texttt{p})$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{c} = \mathit{CMP}(\texttt{sum}_0,\texttt{min}_0)$}
\STATE {$\texttt{index}_1 = \mathit{MUX}(\texttt{c},\texttt{index}_0,i)$}
\STATE {$\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{min}_0,\texttt{sum}_0)$}
\STATE \COMMENT {End of outer loop $i$.}

@@

\STATE \COMMENT {Begin of outer loop $i$.}
\STATE {$\texttt{index}_0[i] = \phi(-1,\texttt{index}_1[i-1])$} 
\STATE {$\texttt{min}_0[i] = \phi(10000, \texttt{min}_1[i-1])$}

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0[i,j] = \phi([0,0,...], \texttt{sum}_1[i,j-1])$}
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUB}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{sum}'_0[i] = \mathit{drop\_dim}(\texttt{sum}_0[i,j],j)$}
\STATE {$\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_0[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}])$}
\STATE {$\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N])$}
\STATE {$\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_0[\stackrel{\rightarrow}{i}])$}
\STATE \COMMENT {End of outer loop $i$.}

@@

Starting at the inner phi-node $\texttt{sum}_0[i,j] = \phi([0,0,...],\texttt{sum}_1[i,j-1])$, the algorithm first computes its closure. The closure amounts to the phi-node itself and $\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$, accounting for the loop-carried dependency of the computation of \texttt{sum}. The algorithm replaces this closure with a FOR loop on $j$ removing vectoriaztion on $j$. Note that the SUB and MUL computations remain outside of the loop as they do not depend on phi-nodes that are part of cycles. The algorithm adds same-level edges, one from $\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = ...$ to the monolithic FOR-loop node, and one from the FOR-loop node to $\texttt{c}[\stackrel{\rightarrow}{i}] = ...$.

@@

\STATE \COMMENT {Begin of outer loop $i$.}
\STATE {$\texttt{index}_0[i] = \phi(-1, \texttt{index}_1[i-1])$} 
\STATE {$\texttt{min}_0[i] = \phi(10000, \texttt{min}_1[i-1])$}

@@

\STATE \COMMENT {Begin of inner loop $j$. Loop is now much "shorter"!}
\STATE {$\texttt{sum}_0[i,j] = \phi([0,0,...], \texttt{sum}_1[i,j-1])$}
\STATE {FOR j=0; j<D; j++} \COMMENT{ Will turn into a MOTION loop.}
\STATE \hspace{0.25cm}{$\texttt{sum}_1[\stackrel{\rightarrow}{i},{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},{j}],\texttt{p}[\stackrel{\rightarrow}{i},{j}])$}
\STATE \COMMENT {End of inner loop $j$.}

@@

Next, analysis moves to outer dimension $i$. There are two phi-nodes, $\texttt{min}_0[i] = \phi(10000,\texttt{min}_1[i-1])$ and $\texttt{index}_0[i] = \phi(-1,\texttt{index}_1[i-1])$.
The closure of the first is 
\[
\begin{array}{l}
\texttt{min}_0[i] = \phi(10000,\texttt{min}_1[i-1]) \\
\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_0[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_0[\stackrel{\rightarrow}{i}])
\end{array}
\]
and the closure of the second one is
\[
\begin{array}{l}
\texttt{index}_0[i] = \phi(-1,\texttt{index}_1[i-1]), \\ 
%\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N]) 
\end{array}
\]

@@

\STATE 
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUB\_SIMD}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL\_SIMD}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$} \\
\STATE {} 
\STATE {$\texttt{sum}_0[i,j] = \phi([0,0,...],\texttt{sum}_1[i,j-1])$}
\STATE {FOR j=0; j<D; j++} \COMMENT{ Turns into a MOTION loop, was $j$-loop.}
\STATE \hspace{0.25cm}{$\texttt{sum}_1[\stackrel{\rightarrow}{i},{j}] = \mathit{ADD\_SIMD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},{j}],\texttt{p}[\stackrel{\rightarrow}{i},{j}])$}
\STATE {} 
\STATE {$\texttt{sum}'_0[i] = \mathit{drop\_dim}(\texttt{sum}_0[i,j],j)$}
\STATE {} 
\STATE {$\texttt{min}_0[i] = \phi(10000,\texttt{min}_1[i-1])$}
\STATE {FOR i=0; i<N; i++} \COMMENT{ Turns into a MOTION loop, was $i$-loop.}
\STATE \hspace{0.25cm}{$\texttt{c}[{i}] = \mathit{CMP}(\texttt{sum}'_0[{i}],\texttt{min}_0[{i}])$}
\STATE \hspace{0.25cm}{$\texttt{min}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{min}_0[{i}],\texttt{sum}'_1[{i}])$}
\STATE {}
\STATE {$\texttt{index}_0[i] = \phi(-1,\texttt{index}_1[i-1])$} 
\STATE {FOR i=0; i<N; i++} \COMMENT{ Turns into a MOTION loop, was $i$-loop.}
\STATE \hspace{0.25cm}{$\texttt{index}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{index}_0[{i}],i)$}
